---
title: "vis_1"
author: "Tong Su"
date: "2024-09-26"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
```
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Making our 1st plot :-)

```{r}
#1
ggplot(weather_df, aes(x=tmin, y=tmax))+
  geom_point()
```


```{r}
#2
weather_df |>
  ggplot(aes(x=tmin, y=tmax))+
  geom_point()
```

```{r}
#3
ggp_weather_scatterplot = 
  weather_df |>
  ggplot(aes(x=tmin, y=tmax))+
  geom_point()

ggp_weather_scatterplot
```

```{r}
weather_df |>
  filter(is.na(tmax))
```

```{r}
#4
weather_df |>
  ggplot(aes(x=tmin, y=tmax, color = name)) +
  geom_point()
```
```{r}
#5
weather_df |>
  ggplot(aes(x=tmin, y=tmax, color = name)) +
  geom_point(alpha = .3, size = .8)
```
```{r}
#6
weather_df |>
  ggplot(aes(x=tmin, y=tmax, color = name)) +
  geom_point(alpha = .3, size = .8) +
  geom_smooth(se=FALSE)
```

Where you define aesthetics can matter
```{r}
#7
weather_df |>
  ggplot(aes(x=tmin, y=tmax)) +
  geom_point(aes(color=name),alpha = .3, size = .8) +
  geom_smooth(se=FALSE)
```

use faceting real quick

```{r}
#10
weather_df |>
  ggplot(aes(x=tmin, y=tmax, color = name)) +
  geom_point(alpha = .3)+
  geom_smooth(se=FALSE)+
  facet_grid(.~name)
```


```{r}
#11
weather_df |>
  ggplot(aes(x=tmin, y=tmax, color = name)) +
  geom_point(alpha = .3)+
  geom_smooth(se=FALSE)+
  facet_grid(name~.)
```

Let's make a somewhat more interesting scatterplot
```{r}
#12
weather_df |>
  ggplot(aes(x=date, y=tmax, color = name)) +
  geom_point()
```

```{r}
#13
weather_df |>
  ggplot(aes(x=date, y=tmax, color = name)) +
  geom_point(alpha=.3)+
  geom_smooth(se=FALSE)
```
```{r}
#14
weather_df |>
  ggplot(aes(x=date, y=tmax, color = name, size = prcp)) +
  geom_point(alpha=.3)+
  geom_smooth(se=FALSE)+
  facet_grid(.~name)
```

Write a code chain that starts with weather_df; focuses only on Central Park, converts temperatures to Fahrenheit, makes a scatterplot of min vs. max temperature, and overlays a linear regression line (using options in geom_smooth()).
```{r}
#15
weather_df |> 
  filter(name == "CentralPark_NY") |>  #720 rows only central park
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32) |> 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE) #linear model
```

##Small things
```{r}
#16
weather_df |>
  ggplot(aes(x=tmin, y=tmax)) +
  geom_point(aes(color=name),alpha = .3, size = .8) +
  geom_smooth(se=FALSE)
```

```{r}
#17
weather_df |>
  ggplot(aes(x=tmin, y=tmax)) +
  geom_hex()
```

Since blue is not a variable in the data set, the point color doesn't show blue.
When a thing is a variable, put it enclosed by ggplot(), for here R thinks that blue is a variable.
```{r}
#18
weather_df |>
  ggplot(aes(x=tmin, y=tmax, color="blue")) +
  geom_point()
```
```{r} 
#19
weather_df |>
  ggplot(aes(x=tmin, y=tmax)) +
  geom_point(color = "pink")
```

##Univariable plots
```{r}
#20
weather_df |>
  ggplot(aes(x=tmin)) +
  geom_histogram()
```

```{r}
#21
weather_df |>
  ggplot(aes(x=tmin, fill=name)) +
  geom_histogram(position = "dodge")
```

How would i fix this? maybe facet
```{r}
#22
weather_df |>
  ggplot(aes(x=tmin, fill=name)) +
  geom_histogram()+
  facet_grid(.~name)
```

maybe a density plot?
```{r}
#23
weather_df |>
  ggplot(aes(x=tmin, fill=name)) +
  geom_density(alpha=.3)
```

##boxplot
```{r}
#24
weather_df |>
  ggplot(aes(x=name, y=tmin)) +
  geom_boxplot()
```
```{r}
#25
weather_df |>
  ggplot(aes(x=name, y=tmin, fill=name)) +
  geom_boxplot()
```

violin plots (for a huge amount of data, violin plot can give you a insight that if there is something strange going on)
```{r}
#26
weather_df |> 
  ggplot(aes(x=name, y=tmin, fill=name))+
  geom_violin()
```

ridge plot 
```{r}
#27
weather_df |> 
  ggplot(aes(x=tmin, y=name))+
  geom_density_ridges()
```


